%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Liam}{Bowen}{ Software Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
(518) 321-5076
Delmar, NY 12054
~
\href{mailto:LiamBowen@gmail.com}{LiamBowen@gmail.com}
\href{http://hut8.io}{hut8.io}
\href{https://github.com/hut8}{github.com/hut8}
\href{https://linkedin.com/in/LiamBowen}{linkedin.com/in/LiamBowen}
~
\section{Programming}
{\color{red} $\varheartsuit$}
ASM (x86/x64)
AngularJS
C
C++
CSS
C\#
FORTRAN
Go
Flask
HTML5
JSON
Java
JavaScript
jQuery
JSON
MongoDB (NoSQL)
Oracle PL/SQL
PHP
Perl
Python
Rails
Ruby
SQL (Various)
Shell (Bash)
VB.NET / VB 6
XML
XSL
\end{aside}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2007-2011}
{Rensselaer Polytechnic Institute}
{B.S. of Computer Science}
{\emph{Incomplete (1-2 semesters remain)}
\\ \emph{Extracurriculars}: Rensselaer Center for Open Source, RPISEC (Computer Security Club), Tau Epsilon Phi Fraternity (social chair) }

%------------------------------------------------

\entry
{2003--2007}
{Bethlehem Central High School}
{High School Diploma}
{\emph{Extracurriculars}: Science Olympiad, National Science Bowl, Masterminds (trivia), Help Desk (Unpaid Intern), Civil Air Patrol
\\ \emph{Awards and Honors}: Science Department Award (x2), Masterminds JV MVP, Science Bowl(Competed Nationally), Science Olympiad}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Professional Experience}

\begin{entrylist}

%------------------------------------------------

\entry
{2013-2014}
{Xerox Litigation Services}
{Albany, NY}
{\emph{Software Engineer (temporary contract through Paladin Consulting)} \\
PHP, MySQL, Oracle PL/SQL, C, JavaScript/jQuery, Ruby, Python and others. Developed new features and fixed bugs in OmniX document review platform. Found and fixed several security flaws. Provided emergency support on-call.
}

\entry
{2009-2010}
{CapitalIQ}
{New York, NY}
{
\emph{Software Engineering Internship + Co-op} \\
ASP.NET, C\# (.NET), JavaScript/jQuery. Offered full-time position as software engineer. Implemented new search engine frontend using jQuery. Made system to automatically provision virtual machines for QA. Wrote automated code-coverage utility with web frontend. Re-architected caching infrastructure using Velocity (like memcached, now part of AppFabric).
}

\entry
{2007-2013}
{Wustefeld Candy Company}
{Green Island, NY}
{
\emph{Software Engineer / Support} \\
Perl, Python, MySQL, C. Mostly independent; briefly on payroll for larger project. Created web application to extend functionality of 20+ year old, telnet-based management software including reverse engineering proprietary database. Supported their network, server and a dozen workstations.
}


\entry
{Fall 2008}
{Rensselaer Polytechnic Institute}
{Troy, NY}
{
\emph{Undergraduate Teaching Assistant} \\
Supervised lab sessions for Computer Science 1; answered questions about C++ and algorithms
}

\end{entrylist}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Open Source}

\textbf{FISS} Fast web server for hosting files from local filesystem with one command. Includes SSH tunneling.
\\
\textbf{Fractus} P2P IM application and protocol with strong cryptographic features.
\\
\textbf{Github Contributions Archive} Tracks 250M contributions from all GitHub users since 2011.
\\
\textbf{Tumblr-Go} Go client for most of Tumblr API. Returns native Go structs.
\\
\textbf{Aliker} Returns similar posts to one provided on Tumblr.
\\


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%% \section{interests}

%% \textbf{professional:} web application engineering, user interface design, security and cryptography, data engineering / analysis, databases
%% \\
%% \textbf{personal:} ham radio, aviation (student pilot), music (violin, mandolin), electronics, open source

\end{document}
